Graph Neural Networks For Multi-Image Matching

### 2019-09-23 latex/iclr2020/main.tex
Fixed up more formatting issues

Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
Methods such as SIFT feature matching \cite{lowe2004distinctive} followed by RANSAC \cite{fischler1981random} have been the standard for decades.
However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
% TODO: Mention trifocal tensors
Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.

However, these multi-view consistency algorithms struggle in distributed and robust settings.
Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed \cite{yi2016lift}.
In this paper, we want to leverage the power of deep representations in order to compute feature descriptors that are robust across multiple views.
% Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
% However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
% Using features designed to deal with these confounding factors improves robustness to them, and learning may improve robustness even further.

@@

%------------------------------------------------------------------------
\begin{figure*}[t]
\begin{center}
  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyMainFigure-v4.pdf}
\end{center}
  \caption{
    An illustration of the approach of this work.
    The Graph Neural Neural Network (GNN) \cite{battaglia2018relational} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
    The GNN operates on an embedding over the vertices of the graph.
    In the figure, the GNN vertex embeddings are represented by different colors.
    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle-consistent representation of the graph adjacency matrix, thus pruning the erroneous matches.
    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and thus do not need ground truth matches.
    In addition, we can use geometric consistency information, such as epipolar constraints, to assist training the network.
  }
\label{fig:pipeline}
\end{figure*}

@@

In this work, we propose to solve these problems using Graph Neural Networks (GNNs) to operate on the correspondence graph.
The proposed method works directly on the correspondence graph, which is agnostic to how the correspondences were computed, thus allowing the algorithm to work in a broad class of environments.
To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
We use an unsupervised loss - the cycle consistency loss - to train the network, and thus avoiding the difficulty of expensive hand labeling.
Geometric consistency losses can aid training, even if such information is not available at test time.
Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss \cite{zhou2015multi, leonardos2016distributed}.
Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than methods which must solve an optimization problem every time.
We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based methods.
Our contributions in this work are:
\begin{itemize}
\item We use a novel architecture to address the multi-image feature matching problem using GNNs with graph embeddings.
\item We introduce an unsupervised cycle consistency loss that does not require labeled correspondences to train.
\item We demonstrate the effectiveness of geometric consistency losses in improving training.
\end{itemize}

@@

\subsection{Feature Matching}
Matching has a rich history of research in computer vision.
Much work has be done using hand-crafted feature descriptors such as SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}.
RANSAC \cite{fischler1981random} is the most widely used robust estimation technique to filter out outliers from the matches.
The combination of RANSAC and hand-crafted feature descriptors has constituted the bulk of the matching literature for the last 40 years.
Finally, graph matching \cite{suh2015subgraph, hu2016distributable} can be used as a final step for more robust matches.

\subsection{Multi-image Matching}
Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3).
Pachauri et al.~\cite{pachauri2013solving} and Arrigoni et al.~\cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
However, the low Gaussian noise assumption is not realistic.
Zhou et al.~\cite{zhou2015multi} and Wang et al.~\cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
Leonardos et al.~\cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
As an alternative to optimization based techniques, Tron et al.~\cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
To the best of our knowledge, we are the first to use neural networks for multi-image matching.

\subsection{Deep Learning for Matching}
Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets \cite{zagoruyko2015learning, yi2016lift, brachmann2017dsac}.
This approach is limited if one do not have the ability to get the ground truth correspondences.
There are other methods to build correspondences such as Choy et al.~\cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
Most similar to our work, Yi et al.~\cite{yi2018learning} attempts to improve correspondences by learning match probabilities for RANSAC for greater robustness and speed.
However, they only focus on two view matching and do not exploit the advantages of the correspondence structure.
Note that while Zhu et al.~\cite{zhu2017unpaired} use cycle consistency in their loss, their method is restricted to pairwise cycle consistency (i.e. enforcing consistency by going back and forth between two images).
We use multi-image cycle consistency, which require consistency between 3 or more images.

\subsection{Graph Neural Networks}
Graph neural networks have recieved more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in Bruna et al.~\cite{bruna2013spectral}, but requires an a-priori known graph structure. 
Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2017semi, scarselli2009graph, gama2018convolutional}.
Most of these methods use polynomials of the graph Laplacian to compute neighborhood averages.
Gama et al.~2018 \cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in Battaglia et al.~\cite{battaglia2018relational}.

@@

Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
An outline of our approach can be seen in figure \ref{fig:pipeline}.
The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
We do this by training the new set of feature embeddings to be cycle consistent.
We formulate this problem in terms of the correspondence graph of the features.
Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$ and implicitly in the subsequent discussions we assume the edges are directed.
For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
Similarly $\mathcal{E}(v)$ is used to denote the edges associated with $v$.
To denote the vertices connected to an edge $e \in \mathcal{E}$ we write $e(v_1, v_2)$.
\subsection{Correspondence Graph}
We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mA$.
The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
While there are many interesting methods for computing these putative correspondences \cite{suh2015subgraph, yi2018learning}, we do not explore them in this work.
Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
The ambiguity in the matches could come from repeated structures in the scene, insufficiently informative low-level feature descriptors, or just an error in the matching algorithm.
Filtering out these noisy matches is our primary learning goal.

@@

First we describe older methods of GNNs to give context, then we describe the method we use in this work.
Many older methods assume we have the adjacency matrix $\mA$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mA$.
However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
There are many variations on non-spectral methods, often which ultimately amount to message passing between vertices of the graph with learned non-linear transformations between various steps \cite{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}.
Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
Most of GNNs used in these works can be expressed mathematically as:
\begin{align*}
\tilde{\vf}_v^{(k+1)} =&\; \sigma\left( b^{(k)} + \mW_0^{k} \vf_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mW_{h}^{k} \vf_{v'}^{(k)} \right) \\
\end{align*}
The weights/biases $\mW_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.

@@

Let $\mM$ be the noiseless set of matches between our features, with $\mM_{ij}$ being the matches between image $i$ and image $j$.
If the pairwise matches are globally consistent, then for all $i, j, k$:
\begin{equation}
\mM_{ij} = \mM_{ik} \mM_{kj}
\label{eq:cycconsist1}
\end{equation}
In other words, the matches between two images stay the same no matter what path is taken to get there. 
This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mX_i$.
Then the cycle consistency constraint becomes:
\begin{equation}
\mM_{ij} = \mX_{i}\mX_{j}^\top
\label{eq:cycconsist2}
\end{equation}

@@

One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
The simplest way to add geometric consistency losses, and the approach we use here, is to use the epipolar constraint.
The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
An illustration of this is provided in figure \ref{fig:geoconsist}, showing how this loss can help reject erroneous points.
Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$: $X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0$.
In this work we use the two pose epipolar constraint \cite{tron2014quotient}:
\begin{equation}
X_{i}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j} = 0
\label{eq:essential_constraint}
\end{equation}
% Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
The constraint assumes that the $X_k$ are calibrated (i.e. the camera intrinsics are known). 
Given our vertex embeddings matrix $\mF_V$, we can formulate a loss between all cameras $i$ and $j$:
\begin{align}
\mathcal{L}_{ij,geom}(\mF_V) = 
&\sum_{v \in \mV(i),u \in \mathcal{V}(j)} (\vf_v \cdot \vf_u) \left|X_{v}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{c_j} X_{u}\right|
\label{eq:geom_cost}
\end{align}
With $\mathcal{V}(i)$ being the vertices associated with camera $i$.
For our purposes, since we use low rank embeddings $\mE_{i}$, $\mE_{j}$, the loss would read (where $c(k)$ is the appropriate camera for point index $k$):
\begin{align} 
\mathcal{L}_{geom}(\mF_V)
=&\; \mathrm{tr}(\mG^\top \mF_V\mF_V^\top) = \sum_{k,l} (\mF_V)_{k} \cdot (\mF_V)_{l} (\mG)_{kl} \label{eq:geom_cost2} \\
(\mG)_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
\end{align}

\begin{table*}[t]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
Method (6 Views)                                     & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
\hline\hline
MatchALS 15 Iterations & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.074 $\pm$ 0.008 \\ \hline
MatchALS 25 Iterations & 0.059 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.921 $\pm$ 0.077 & 0.143 $\pm$ 0.064 \\ \hline
MatchALS 35 Iterations & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.139 $\pm$ 0.041 \\ \hline
MatchALS 50 Iterations & 0.029 $\pm$ 0.017 & 0.008 $\pm$ 0.005 & 0.905 $\pm$ 0.068 & 0.260 $\pm$ 0.048 \\ \hline
PGDDS0 15 Iterations   & 0.017 $\pm$ 0.002 & 0.007 $\pm$ 0.001 & 0.918 $\pm$ 0.087 & 0.796 $\pm$ 0.147 \\ \hline
PGDDS0 25 Iterations   & 0.016 $\pm$ 0.002 & 0.007 $\pm$ 0.002 & 0.919 $\pm$ 0.087 & 1.670 $\pm$ 0.328 \\ \hline
PGDDS0 50 Iterations   & 0.015 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.920 $\pm$ 0.087 & 3.363 $\pm$ 0.528 \\ \hline
Spectral               & 0.073 $\pm$ 0.006 & 0.027 $\pm$ 0.003 & 0.921 $\pm$ 0.083 & 0.036 $\pm$ 0.005 \\ \hline
\textbf{GNN (ours)}    & 0.044 $\pm$ 0.005 & 0.031 $\pm$ 0.005 & 0.872 $\pm$ 0.081 & 0.765 $\pm$ 0.046 \\ \hline

\hline\hline
Method (10 Views)                                   & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
\hline\hline
MatchALS 15 Iterations & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.142 $\pm$ 0.009 \\ \hline
MatchALS 25 Iterations & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.228 $\pm$ 0.014 \\ \hline
MatchALS 35 Iterations & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.355 $\pm$ 0.073 \\ \hline
MatchALS 50 Iterations & 0.045 $\pm$ 0.012 & 0.011 $\pm$ 0.004 & 0.914 $\pm$ 0.051 & 0.455 $\pm$ 0.022 \\ \hline
PGDDS 15 Iterations    & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 1.225 $\pm$ 0.159 \\ \hline
PGDDS 25 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.904 $\pm$ 0.061 & 2.637 $\pm$ 0.357 \\ \hline
PGDDS 50 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.905 $\pm$ 0.061 & 6.116 $\pm$ 1.009 \\ \hline
Spectral               & 0.073 $\pm$ 0.005 & 0.029 $\pm$ 0.002 & 0.912 $\pm$ 0.057 & 0.081 $\pm$ 0.021 \\ \hline
\textbf{GNN (ours)}    & 0.053 $\pm$ 0.006 & 0.035 $\pm$ 0.005 & 0.872 $\pm$ 0.061 & 2.438 $\pm$ 0.070 \\ \hline

@@

The network was implemented using the code provided by \cite{battaglia2018relational} using Tensorflow \cite{tensorflow2015} 1.11.
Our network has 16 layers, with 8 message passing operations placed every other layer.
All layers were simple Multi-layer Perceptrons, with no batch norm.
The network was trained with the Adam optimizer \cite{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers (all possible pairs).

>>>>

Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
Methods such as SIFT feature matching (\cite{lowe2004distinctive}) followed by RANSAC (\cite{fischler1981random}) have been the standard for decades.
However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
% TODO: Mention trifocal tensors
Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.

However, these multi-view consistency algorithms struggle in distributed and robust settings.
Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed (\cite{yi2016lift}).
In this paper, we want to leverage the power of deep representations in order to compute feature descriptors that are robust across multiple views.
% Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
% However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
% Using features designed to deal with these confounding factors improves robustness to them, and learning may improve robustness even further.

@@

%------------------------------------------------------------------------
\begin{figure*}[t]
\begin{center}
  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyMainFigure-v4.pdf}
\end{center}
  \caption{
    An illustration of the approach of this work.
    The Graph Neural Neural Network (GNN) (\cite{battaglia2018relational}) takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
    The GNN operates on an embedding over the vertices of the graph.
    In the figure, the GNN vertex embeddings are represented by different colors.
    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle-consistent representation of the graph adjacency matrix, thus pruning the erroneous matches.
    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and thus do not need ground truth matches.
    In addition, we can use geometric consistency information, such as epipolar constraints, to assist training the network.
  }
\label{fig:pipeline}
\end{figure*}

@@

In this work, we propose to solve these problems using Graph Neural Networks (GNNs) to operate on the correspondence graph.
The proposed method works directly on the correspondence graph, which is agnostic to how the correspondences were computed, thus allowing the algorithm to work in a broad class of environments.
To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
We use an unsupervised loss - the cycle consistency loss - to train the network, and thus avoiding the difficulty of expensive hand labeling.
Geometric consistency losses can aid training, even if such information is not available at test time.
Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss (\cite{zhou2015multi, leonardos2016distributed}).
Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than methods which must solve an optimization problem every time.
We perform experiments on the Rome16K dataset (\cite{li2010location}) to test the effectiveness of our method compared to optimization based methods.
Our contributions in this work are:
\begin{itemize}
\item We use a novel architecture to address the multi-image feature matching problem using GNNs with graph embeddings.
\item We introduce an unsupervised cycle consistency loss that does not require labeled correspondences to train.
\item We demonstrate the effectiveness of geometric consistency losses in improving training.
\end{itemize}

@@

\subsection{Feature Matching}
Matching has a rich history of research in computer vision.
Much work has be done using hand-crafted feature descriptors such as SIFT (\cite{lowe2004distinctive}), SURF (\cite{bay2006surf}), BRIEF (\cite{calonder2012brief}), or ORB (\cite{mur2015orb}).
RANSAC \cite{fischler1981random} is the most widely used robust estimation technique to filter out outliers from the matches.
The combination of RANSAC and hand-crafted feature descriptors has constituted the bulk of the matching literature for the last 40 years.
Finally, graph matching (\cite{suh2015subgraph, hu2016distributable}) can be used as a final step for more robust matches.

\subsection{Multi-image Matching}
Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3).
\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
However, the low Gaussian noise assumption is not realistic.
\cite{zhou2015multi} and \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
\cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
To the best of our knowledge, we are the first to use neural networks for multi-image matching.

\subsection{Deep Learning for Matching}
Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets such as \cite{zagoruyko2015learning}; \cite{yi2016lift}; and \cite{brachmann2017dsac}.
This approach is limited if one do not have the ability to get the ground truth correspondences.
There are other methods to build correspondences such as \cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
Most similar to our work, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for RANSAC for greater robustness and speed.
However, they only focus on two view matching and do not exploit the advantages of the correspondence structure.
Note that while \cite{zhu2017unpaired} use cycle consistency in their loss, their method is restricted to pairwise cycle consistency (i.e. enforcing consistency by going back and forth between two images).
We use multi-image cycle consistency, which require consistency between 3 or more images.

\subsection{Graph Neural Networks}
Graph neural networks have recieved more attention recently e.g. \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional}; and \cite{battaglia2018relational}.
Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in \cite{bruna2013spectral}, but requires an a-priori known graph structure. 
Non-spectral methods do not require a-priori knowledge, as seen in \cite{bronstein2017geometric, kipf2017semi, scarselli2009graph}; and \cite{gama2018convolutional}.
Most of these methods use polynomials of the graph Laplacian to compute neighborhood averages.
\cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in \cite{battaglia2018relational}.

@@

Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
An outline of our approach can be seen in figure \ref{fig:pipeline}.
The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
We do this by training the new set of feature embeddings to be cycle consistent.
We formulate this problem in terms of the correspondence graph of the features.
Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$ and implicitly in the subsequent discussions we assume the edges are directed.
For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
Similarly $\mathcal{E}(v)$ is used to denote the edges associated with $v$.
To denote the vertices connected to an edge $e \in \mathcal{E}$ we write $e(v_1, v_2)$.
\subsection{Correspondence Graph}
We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mA$.
The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
While there are many interesting methods for computing these putative correspondences (\cite{suh2015subgraph, yi2018learning}), we do not explore them in this work.
Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
The ambiguity in the matches could come from repeated structures in the scene, insufficiently informative low-level feature descriptors, or just an error in the matching algorithm.
Filtering out these noisy matches is our primary learning goal.

@@

First we describe older methods of GNNs to give context, then we describe the method we use in this work.
Many older methods assume we have the adjacency matrix $\mA$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mA$.
However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
There are many variations on non-spectral methods, often which ultimately amount to message passing between vertices of the graph with learned non-linear transformations between various steps (\cite{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}).
Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
Most of GNNs used in these works can be expressed mathematically as:
\begin{align*}
\tilde{\vf}_v^{(k+1)} =&\; \sigma\left( b^{(k)} + \mW_0^{k} \vf_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mW_{h}^{k} \vf_{v'}^{(k)} \right) \\
\end{align*}
The weights/biases $\mW_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.

@@

Let $\mM$ be the noiseless set of matches between our features, with $\mM_{ij}$ being the matches between image $i$ and image $j$.
If the pairwise matches are globally consistent, then for all $i, j, k$:
\begin{equation}
\mM_{ij} = \mM_{ik} \mM_{kj}
\label{eq:cycconsist1}
\end{equation}
In other words, the matches between two images stay the same no matter what path is taken to get there. 
This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency (\cite{zhou2015multi, wang2017multi, leonardos2016distributed}).
Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mX_i$.
Then the cycle consistency constraint becomes:
\begin{equation}
\mM_{ij} = \mX_{i}\mX_{j}^\top
\label{eq:cycconsist2}
\end{equation}

@@

One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
The simplest way to add geometric consistency losses, and the approach we use here, is to use the epipolar constraint.
The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
An illustration of this is provided in figure \ref{fig:geoconsist}, showing how this loss can help reject erroneous points.
Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$: $X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0$.
In this work we use the two pose epipolar constraint (\cite{tron2014quotient}):
\begin{equation}
X_{i}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j} = 0
\label{eq:essential_constraint}
\end{equation}
% Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
The constraint assumes that the $X_k$ are calibrated (i.e. the camera intrinsics are known). 
Given our vertex embeddings matrix $\mF_V$, we can formulate a loss between all cameras $i$ and $j$:
\begin{align}
\mathcal{L}_{ij,geom}(\mF_V) = 
&\sum_{v \in \mV(i),u \in \mathcal{V}(j)} (\vf_v \cdot \vf_u) \left|X_{v}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{c_j} X_{u}\right|
\label{eq:geom_cost}
\end{align}
With $\mathcal{V}(i)$ being the vertices associated with camera $i$.
For our purposes, since we use low rank embeddings $\mE_{i}$, $\mE_{j}$, the loss would read (where $c(k)$ is the appropriate camera for point index $k$):
\begin{align} 
\mathcal{L}_{geom}(\mF_V)
=&\; \mathrm{tr}(\mG^\top \mF_V\mF_V^\top) = \sum_{k,l} (\mF_V)_{k} \cdot (\mF_V)_{l} (\mG)_{kl} \label{eq:geom_cost2} \\
(\mG)_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
\end{align}

\begin{table*}[t]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
Method (6 Views)                                     & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
\hline\hline
MatchALS 15 Iterations & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.074 $\pm$ 0.008 \\ \hline
MatchALS 35 Iterations & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.139 $\pm$ 0.041 \\ \hline
MatchALS 50 Iterations & 0.029 $\pm$ 0.017 & 0.008 $\pm$ 0.005 & 0.905 $\pm$ 0.068 & 0.260 $\pm$ 0.048 \\ \hline
PGDDS0 15 Iterations   & 0.017 $\pm$ 0.002 & 0.007 $\pm$ 0.001 & 0.918 $\pm$ 0.087 & 0.796 $\pm$ 0.147 \\ \hline
PGDDS0 25 Iterations   & 0.016 $\pm$ 0.002 & 0.007 $\pm$ 0.002 & 0.919 $\pm$ 0.087 & 1.670 $\pm$ 0.328 \\ \hline
PGDDS0 50 Iterations   & 0.015 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.920 $\pm$ 0.087 & 3.363 $\pm$ 0.528 \\ \hline
Spectral               & 0.073 $\pm$ 0.006 & 0.027 $\pm$ 0.003 & 0.921 $\pm$ 0.083 & 0.036 $\pm$ 0.005 \\ \hline
\textbf{GNN (ours)}    & 0.044 $\pm$ 0.005 & 0.031 $\pm$ 0.005 & 0.872 $\pm$ 0.081 & 0.765 $\pm$ 0.046 \\ \hline

\hline\hline
Method (10 Views)                                   & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
\hline\hline
MatchALS 25 Iterations & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.228 $\pm$ 0.014 \\ \hline
MatchALS 35 Iterations & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.355 $\pm$ 0.073 \\ \hline
MatchALS 50 Iterations & 0.045 $\pm$ 0.012 & 0.011 $\pm$ 0.004 & 0.914 $\pm$ 0.051 & 0.455 $\pm$ 0.022 \\ \hline
PGDDS 15 Iterations    & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 1.225 $\pm$ 0.159 \\ \hline
PGDDS 25 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.904 $\pm$ 0.061 & 2.637 $\pm$ 0.357 \\ \hline
PGDDS 50 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.905 $\pm$ 0.061 & 6.116 $\pm$ 1.009 \\ \hline
Spectral               & 0.073 $\pm$ 0.005 & 0.029 $\pm$ 0.002 & 0.912 $\pm$ 0.057 & 0.081 $\pm$ 0.021 \\ \hline
\textbf{GNN (ours)}    & 0.053 $\pm$ 0.006 & 0.035 $\pm$ 0.005 & 0.872 $\pm$ 0.061 & 2.438 $\pm$ 0.070 \\ \hline

@@

The network was implemented using the code provided by \cite{battaglia2018relational} using Tensorflow 1.11 (\cite{tensorflow2015}).
Our network has 16 layers, with 8 message passing operations placed every other layer.
All layers were simple Multi-layer Perceptrons, with no batch norm.
The network was trained with the Adam optimizer (\cite{kingma2014adam}) with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers (all possible pairs).
